The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-19 Background/pbm_bg.tex
Fixed issues reported by chrisper (bugs in writing)

E-Mail Header Injection belongs to a broad class of vulnerabilities known simply as injection attacks. However, unlike its more popular siblings, SQL injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting (XSS) \cite{Injection1}, \cite{KleinAmit} or even HTTP Header Injection~\cite{sessionride}, relatively little research is available on E-Mail Header Injection.

>>>>

E-Mail Header Injection belongs to a broad class of vulnerabilities known simply as injection attacks. However, unlike its more popular siblings, SQL injection~\cite{sql1}, \cite{sql0}, \cite{sql2}, Cross-Site Scripting (XSS)~\cite{Injection1}, \cite{KleinAmit} or even HTTP Header Injection~\cite{sessionride}, relatively little research is available on E-Mail Header Injection.

### 2016-05-19 Discussion/limits.tex
Fixed issues reported by chrisper (bugs in writing)

\subsection[Limitations]{Limitations of the Project}
\label{limitations}
	This section discusses the limitations of our project. The following list, although not exhaustive, goes into some of them in detail: 
	\begin{itemize}
		\item Bot Blockers and CAPTCHAs\\
		Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.\ mechanisms built-in to a website to prevent automated crawls or form submissions. Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3}, \cite{captchas2}.

@@

        \item Black-box Testing\\
        The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section \ref{sys:appr}. However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers). We have to manually e-mail the developers to get this feedback.

       	\item \label{issues:fpr}False Positive rate for the E-Mail Field Checker\\
       	As discussed in Section \ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}. This might result in a false positive in certain forms, like the one shown in Listing. \ref{code:false_positive}.

>>>>

\subsection[Limitations]{Limitations of the Project}
\label{limitations}
	This section discusses the limitations of our project. The following list, although not exhaustive, goes into some of them in detail:
	\begin{itemize}
		\item Bot Blockers and CAPTCHAs\\
		Because our system is fully automated, it is also susceptible to being stopped by `bot-blockers' i.e.,\ mechanisms built-in to a website to prevent automated crawls or form submissions. Measures like CAPTCHA (Completely Automated Public Turing test to tell Computers and Humans Apart) and hidden form fields are often used to detect bots~\cite{captchas3}, \cite{captchas2}.

@@

        \item Black-box Testing\\
        The approach that we have selected --- Black-box testing --- is highly beneficial as explained in Section~\ref{sys:appr}. However, it also has a drawback in that we cannot verify whether the reported vulnerability exists in the source code or is a feature of the website (e.g., the website allows users to send bulk e-mail, adding as many \texttt{cc} or \texttt{bcc} headers). We have to manually e-mail the developers to get this feedback.

       	\item \label{issues:fpr}False Positive rate for the E-Mail Field Checker\\
       	As discussed in Section~\ref{Comp:EMFC}, we only search for the words \texttt{email}, \texttt{mail} or \texttt{e-mail} (case insensitive) inside the forms to detect the presence of e-mail fields, instead of searching for an \colorbox{lightgray}{\lstinline{<input type = email>}}. This might result in a false positive in certain forms, like the one shown in Listing~\ref{code:false_positive}.

### 2016-05-19 System/assumptions.tex
HUGE changes
chap6,7,8 prelim edits
Fixed issues reported by chrisper (bugs in writing)

\subsection{Assumptions}
We made certain assumptions while building the system. This section describes the assumptions and explores to what extent these hold true:
\begin{enumerate}
	\item \textbf{Crawler is not blocked by firewalls}\\
	This is a requisite for our system to work. If the Crawler is blocked for any reason, we do not get the data feed for our system, and without this input, it is almost impossible to set our system up.
	\item \textbf{The Crawler feed is an ideal representation of the World Wide Web} \\
	This is a reasonable expectation, albeit an unrealistic one.

@@

	However, this assumption is reasonable due to the `Law of averages' \cite{wiki:Law_of_averages}, the `Law of big numbers' \cite{wiki:Law_of_large_numbers}, and the concept of `Regression to the mean' \cite{wiki:Regression_toward_the_mean}. Simply stated, a crawl of this large magnitude should give us a very distributed sample of the overall Web, eventually converging to the average of all websites in existence.

@@

That concludes our discussion about the design of the system. To recap, we discussed our approach, the system architecture and how the components fit into our architecture. We also discussed the issues faced, and the assumptions that we made while building the system. %The next chapter describes, in brief, the experimental setup we used for our system.

>>>>

\subsection{Assumptions}
In addition to the limitations that were already discussed, we made certain assumptions while building the system. This section describes the assumptions and explores to what extent these hold true:
\begin{enumerate}
	\item \textbf{Crawler is not blocked by firewalls}\\
	This is a requisite for our system to work. If the Crawler is blocked for any reason, we do not get the data feed for our system, and without this input, it is almost impossible to set our system up.

	\item \textbf{The Crawler feed is an ideal representation of the World Wide Web} \\
	This is a reasonable expectation, albeit an unrealistic one.

@@

	However, this assumption is reasonable due to the `Law of averages'~\cite{wiki:Law_of_averages}, the `Law of big numbers'~\cite{wiki:Law_of_large_numbers}, and the concept of `Regression to the mean'~\cite{wiki:Regression_toward_the_mean}. Simply stated, a crawl of this large magnitude should give us a very distributed sample of the overall Web, eventually converging to the average of all websites in existence.

@@

That concludes our discussion about the design of the system. To recap, we discussed our approach, the system architecture and how the components fit into our architecture. We also discussed the issues faced, and the assumptions that we made while building the system. %The next section describes, in brief, the experimental setup we used for our system.

### 2016-05-19 System/components.tex
Fixed issues reported by chrisper (bugs in writing)

Compared to searching for explicit e-mail fields, by searching for the presence of the words \texttt{e-mail}, \texttt{mail} or \texttt{email} in the form, we are assured very few false negatives. This is because our system is bound to find e-mail fields with their \texttt{type}, \texttt{name}, or \texttt{id} set to one of these words. The system is also substantially faster as we do not have to parse the individual form fields at this point in the pipeline. However, despite the advantages, this might also lead to a false positive rate. We discuss this possibility in detail in Section \ref*{issues:fpr} - Design Issues.

@@

\paragraph{Analyzing e-mail with payloads}
The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts. These e-mails were received due to injecting the malicious payloads that were discussed in Section. \ref{Comp:Fuzzer:mp}. Analysis of these e-mails is considerably simpler than that of the regular e-mails. This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
\paragraph{Detecting injected \texttt{bcc} headers}
As discussed in the payloads section (\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field. Thus, we simply parse the E-Mails and store them in the Database.

\label{analyze:detect_x_check}
\paragraph{Detecting injected \texttt{x-check} headers}
E-Mails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of e-mails.
These e-mails could have been generated due to two reasons:
\begin{enumerate}
	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending e-mails only to the \texttt{nuser} account. These e-mails then act as proof that the vulnerability was not found on the given website.
	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.\ Python's default behavior when it encounters duplicate headers. In this case, we check whether the e-mail contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability, and we store it in the database.
\end{enumerate}

>>>>

Compared to searching for explicit e-mail fields, by searching for the presence of the words \texttt{e-mail}, \texttt{mail} or \texttt{email} in the form, we are assured very few false negatives. This is because our system is bound to find e-mail fields with their \texttt{type}, \texttt{name}, or \texttt{id} set to one of these words. The system is also substantially faster as we do not have to parse the individual form fields at this point in the pipeline. However, despite the advantages, this might also lead to a false positive rate. We discuss this possibility in detail in Section~\ref*{issues:fpr} - Design Issues.

@@

\paragraph{Analyzing e-mail with payloads}
The `e-mails with payloads' refer to e-mails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts. These e-mails were received due to injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer:mp}. Analysis of these e-mails is considerably simpler than that of the regular e-mails. This is due to the fact that this involves lesser processing of the contents of the e-mail compared to the previous section.
\paragraph{Detecting injected \texttt{bcc} headers}
As discussed in the payloads section~(\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the e-mails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field. Thus, we simply parse the E-Mails and store them in the Database.

\label{analyze:detect_x_check}
\paragraph{Detecting injected \texttt{x-check} headers}
E-Mails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of e-mails.
These e-mails could have been generated due to two reasons:
\begin{enumerate}
	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending e-mails only to the \texttt{nuser} account. These e-mails then act as proof that the vulnerability was not found on the given website.
	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.,\ Python's default behavior when it encounters duplicate headers. In this case, we check whether the e-mail contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability, and we store it in the database.
\end{enumerate}

### 2016-05-19 System/issues.tex
Fixed issues reported by chrisper (bugs in writing)

	\item Parallelism for the system\\
	\label{issues:parallel}
	Every component in the pipeline benefits hugely from parallel processing of the data. However, Python's GIL (Global Interpreter Lock) does not allow the running of multiple native threads concurrently. To overcome this, we used a Celery task queue (discussed in Section \ref{exp:Celery}), which allowed a level of parallelism that Python does not provide by default. Even though this makes the system faster than a single-threaded approach, it still leaves room for improvement in terms of performance. Despite the speed drop that results from lack of full parallelism, we chose to go with Python, for the raw power it provides, its text processing capabilities, PCRE (Perl Compatible Regular Expressions) compatibility, and the numerous libraries available for parsing HTML, interfacing with databases and generating HTTP requests.

@@

	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{action=mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=./mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=http://website.com/mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=www.website.com/mail.php}}
	\end{itemize}
	Add to this, if the form is a self-referencing form\,\footnotemark, and is present in mail.php, the following are equivalent to the above URLs as well:
	\footnotetext{A self-referencing form is one which submits the form data to itself. It includes logic to both display the form and process it. It is a \emph{very} common feature in PHP-based scripts.}
	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{action=""}}
		\item \colorbox{lightgray}{\lstinline{action=#}}
		\item \texttt{action} is completely omitted
	\end{itemize}
	Also, relative URLs pose another problem. If the URL of the form page ends with `/' and the \texttt{action} specifies a path starting with `/' (illustrated in Listing \ref{issues:url}), we would need to strip one of the two slashes. This increases the overall complexity of our URL generator, as we have to account for all these possibilities.

>>>>

	\item Parallelism for the system\\
	\label{issues:parallel}
	Every component in the pipeline benefits hugely from parallel processing of the data. However, Python's GIL (Global Interpreter Lock) does not allow the running of multiple native threads concurrently. To overcome this, we used a Celery task queue (discussed in Section~\ref{exp:Celery}), which allowed a level of parallelism that Python does not provide by default. Even though this makes the system faster than a single-threaded approach, it still leaves room for improvement in terms of performance. Despite the speed drop that results from lack of full parallelism, we chose to go with Python, for the raw power it provides, its text processing capabilities, PCRE (Perl Compatible Regular Expressions) compatibility, and the numerous libraries available for parsing HTML, interfacing with databases and generating HTTP requests.

@@

	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{action=mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=./mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=http://website.com/mail.php}}
		\item \colorbox{lightgray}{\lstinline{action=www.website.com/mail.php}}
	\end{itemize}
	Add to this, if the form is a self-referencing form\,\footnotemark, and is present in mail.php, the following are equivalent to the above URLs as well:
	\footnotetext{A self-referencing form is one which submits the form data to itself. It includes logic to both display the form and process it. It is a \emph{very} common feature in PHP-based scripts.}
	\begin{itemize}
		\item \colorbox{lightgray}{\lstinline{action=""}}
		\item \colorbox{lightgray}{\lstinline{action=#}}
		\item \texttt{action} is completely omitted
	\end{itemize}
	Also, relative URLs pose another problem. If the URL of the form page ends with `/' and the \texttt{action} specifies a path starting with `/' (illustrated in Listing~\ref{issues:url}), we would need to strip one of the two slashes. This increases the overall complexity of our URL generator, as we have to account for all these possibilities.

### 2016-05-19 System/sys_arch.tex
Fixed issues reported by chrisper (bugs in writing)

\subsection{System Architecture}
\label{sys:arch}
The black-box testing system can be divided broadly into two modules; Data Gathering and Payload Injection.
\begin{enumerate}
	\item Data Gathering\\
	The Data Gathering module is primarily responsible for the following activities:
	\begin{itemize}
		\item Interface with the Crawler (Section \ref{Comp:Crawler}) and receive the URLs.
		\item Parse the HTML for the corresponding URL and store the relevant form data (Section \ref{Comp:FP}).
		\item Check for the presence of forms that allow the user to send/receive e-mail, and store references to these forms (Section \ref{Comp:EMFC}).
	\end{itemize} 
	\item Payload Injection\\
	The Payload Injection module is primarily responsible for the following activities:
	\begin{itemize}
		\item Retrieve the forms that allow users of a website to send/receive e-mail and reconstruct these forms (Section \ref{Comp:EMFR}).
		\item Inject these forms with benign data (non-malicious payloads) and generate an HTTP request to the corresponding URL (Section \ref{Comp:Fuzzer:nmp}).
		\item Analyze the e-mails, extracting the header fields and checking for the presence of the injected payloads (Section \ref{Comp:EMA}).
		\item Inject the forms that sent us e-mails with malicious payloads, and generate an HTTP request to the corresponding URL to check if E-Mail Header Injection vulnerability exists in that form (Section \ref{Comp:Fuzzer:mp}).
	\end{itemize} 
	The functionality of each component is discussed further in the `Components' section (Section~\ref{Comp}). The Payload Injection pipeline is not a linear, but cyclic process, as we inject different payloads and analyze the received e-mails.
\end{enumerate}

>>>>

\subsection{System Architecture}
\label{sys:arch}
The black-box testing system can be divided broadly into two modules; Data Gathering and Payload Injection.
\begin{enumerate}
	\item Data Gathering\\
	The Data Gathering module is primarily responsible for the following activities:
	\begin{itemize}
		\item Interface with the Crawler (Section~\ref{Comp:Crawler}) and receive the URLs.
		\item Parse the HTML for the corresponding URL and store the relevant form data (Section~\ref{Comp:FP}).
		\item Check for the presence of forms that allow the user to send/receive e-mail, and store references to these forms (Section~\ref{Comp:EMFC}).
	\end{itemize} 
	\item Payload Injection\\
	The Payload Injection module is primarily responsible for the following activities:
	\begin{itemize}
		\item Retrieve the forms that allow users of a website to send/receive e-mail and reconstruct these forms (Section~\ref{Comp:EMFR}).
		\item Inject these forms with benign data (non-malicious payloads) and generate an HTTP request to the corresponding URL (Section~\ref{Comp:Fuzzer:nmp}).
		\item Analyze the e-mails, extracting the header fields and checking for the presence of the injected payloads (Section~\ref{Comp:EMA}).
		\item Inject the forms that sent us e-mails with malicious payloads, and generate an HTTP request to the corresponding URL to check if E-Mail Header Injection vulnerability exists in that form (Section~\ref{Comp:Fuzzer:mp}).
	\end{itemize} 
	The functionality of each component is discussed further in the `Components' section (Section~\ref{Comp}). The Payload Injection pipeline is not a linear, but cyclic process, as we inject different payloads and analyze the received e-mails.
\end{enumerate}

### 2016-05-19 introduction.tex
fixed citation spaces
Fixed issues reported by chrisper (bugs in writing)

	Since attackers typically masquerade themselves as users of the system, if user input is to be trusted, then developers need to have proper sanitization routines in place. Many different injection attacks such as SQL injection or cross-site scripting (XSS) \cite{OWASPT10} are possible due to improper sanitization of user input.

	Our research focuses on a lesser known injection attack known as E-Mail Header Injection. E-Mail Header Injection can be considered as the e-mail equivalent of HTTP Header Injection vulnerability \cite{wiki:HTTP_headerinjection}. The vulnerability exists in the reference implementation of the built-in \texttt{mail} functionality in popular languages like PHP, Java, Python, and Ruby. With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an e-mail message --- with the potential to alter the contents of the e-mail message --- while still appearing to be from a legitimate source.

>>>>

	Since attackers typically masquerade themselves as users of the system, if user input is to be trusted, then developers need to have proper sanitization routines in place. Many different injection attacks such as SQL injection or cross-site scripting (XSS)~\cite{OWASPT10} are possible due to improper sanitization of user input.

	Our research focuses on a lesser known injection attack known as E-Mail Header Injection. E-Mail Header Injection can be considered as the e-mail equivalent of HTTP Header Injection vulnerability~\cite{wiki:HTTP_headerinjection}. The vulnerability exists in the reference implementation of the built-in \texttt{mail} functionality in popular languages like PHP, Java, Python, and Ruby. With the proper injection string, this vulnerability can be exploited to inject additional headers and/or modify existing headers in an e-mail message --- with the potential to alter the contents of the e-mail message --- while still appearing to be from a legitimate source.

### 2016-05-19 rel_work.tex
Fixed issues reported by chrisper (bugs in writing)

The attack described by Terada~\cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g. \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism. The paper also describes proof-of-concept attacks against certain mailing libraries like \texttt{Ruby Mail} and \texttt{JavaMail}. This attack, although trying to achieve a similar result, is distinctly different from ours. The paper by itself makes this observation and discusses why it is different from E-Mail Header Injection.

@@

Another blog post written by user Voxel@Night on Vexatious Tendencies~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes this vulnerability to be present. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plug-in to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}'' \cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section. \ref{Comp:Fuzzer:mp}).

>>>>

The attack described by Terada~\cite{Terada2015} is one that attacks the underlying SMTP mail servers by injecting SMTP commands (which are closely related to E-Mail Headers and usually have a one-to-one mapping, e.g., \texttt{To} e-mail header has a corresponding \texttt{To} SMTP header) to exploit the SMTP server's pipelining mechanism. The paper also describes proof-of-concept attacks against certain mailing libraries like \texttt{Ruby Mail} and \texttt{JavaMail}. This attack, although trying to achieve a similar result, is distinctly different from ours. The paper by itself makes this observation and discusses why it is different from E-Mail Header Injection.

@@

Another blog post written by user Voxel@Night on Vexatious Tendencies~\cite{Tendencies2014}, recounts an actual attack against a WordPress plugin, \texttt{Contact Form}, with a proof of concept\footnotemark. It also showcases the vulnerable code in the plugin that causes this vulnerability to be present. However, this article targets just one plugin and does not aim to find the prevalence of said plugin usage. Neither does it inform the creators of the plugin to fix the discovered vulnerability.
\footnotetext{Note that this plugin is used actively on 300,000 websites (according to~\cite{BestWebSoft2016}), but is yet to be fixed.}
The vulnerability was described briefly by Stuttard and Pinto in their book, ``\emph{The Web Application Hacker's Handbook: Discovering and Exploiting Security Flaws}''~\cite{stuttard2011web}. The book, however, does not go into detail on either the attack or the ways to mitigate such an attack. Our work, on the other hand discusses the means to mitigate the attack. We also describe, in detail, the payloads that can be used and the need for varying the payloads (Section~\ref{Comp:Fuzzer:mp}).
